Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-06-11 tse19/main.tex
update

\noindent\emph{Adoption.}~ We considered two aspects in measuring technology
adoption.  First, we measured usage of parallelism in open-source projects.
Then, we ran a survey with developers to understand the reasons that could
explain resistance to using the technology.\Comment{ For the quantitative
analysis we checked both statically (parsing build files) and dynamically
(monitoring execution of build files) for the presence of parallelization.}
Considering only the projects whose test suites take longer than a minute to
run, we found that only \percentParallelUpdated{} of them use parallelism.  We
also contacted developers from a selection of costly projects that did not use
parallelization to understand the reasons for not using parallelization.\textcolor{red}{[S.J: nao fizemos isso.]}
Dealing with concurrency-related issues (\eg{}, the extra work to organize test
suite to avoid concurrency errors) and the availability of continuous
integration services were the most frequently answered reasons for not
considering parallelization.

@@

We ran the test suite for each subject three times, reporting averaged
execution times in three ranges: tests that run within a minute
(\shortg{}), tests that run in one to five minutes (\medg{}), and
tests that run in five or more minutes (\longg{}). Figure~\ref{fig:rq1-barplot} shows the number of projects in
each group.  As expected, \longg{} and \medg{} projects do not occur
as frequently as \shortg{} projects.  However, they do occur in
relatively high numbers.
Figure~\ref{fig:rq1-boxplot} shows the distribution of execution time of
test suites in each of these groups.
Note that the y-ranges are different.
The distribution associated with the \shortg{} group is the most
unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
group}.
The test suites in this group ran in 15 or less seconds for
over 75\% of the cases.\Comment{  Such scenarios constitute the majority of the
cases we analyzed.} Considering the groups \medg{} and \longg{},
however, we found many costly executions.  Nearly 75\% of the projects
from the \medg{} group take 3.5 or more minutes to run and nearly 75\% of
the projects from the \longg{} group take $\sim$20 minutes to run.  We
found cases in the \longg{} group were execution takes more than 50 minutes
to complete, as can be observed from the outliers in the boxplot.

@@

Column ``\emph{Subject}'' indicates the name of the project, column
\begin{wraptable}{r}{5cm}
\vspace{-4mm}
\caption{Subjects with parallel test execution enabled by default.}
\label{tab:freqmodes-dynamic}
\footnotesize
\centering
\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{llcr}
\toprule
\multirow{2}{*}{\emph{Group}} & \multirow{2}{*}{\emph{Subject}} & \emph{\# of} & \multirow{2}{*}{\emph{Mode}}\\%
   & & \emph{modules} &\\%
\midrule%
Medium & Californium & 2/20 & C2\\%
Medium & Chaos & 1/1 & C2\\%
Long & \Comment{apache} Flink & 66/74 & FC0\\%
Long & \Comment{apache logging-}Log4J2 & 25/28 & FC0\\%
Long & \Comment{javaslang }Javaslang & 3/3 & C3\\%
Medium & Jcabi \Comment{jcabi-github} & 1/1 & C3\\%
Long & \Comment{hazelcast hazelcast-}Jet & 6/7 & FC0\\%
Long & \Comment{apache} Mahout & 8/9 & FC0\\%
Long & \Comment{jankotek} MapDB & 1/1 & C3\\%
Medium & \Comment{apache} OpenNLP & 4/4 & FC0\\%
Medium & \Comment{yegor256} Rultor & 1/1 & C3\\%
Medium & \Comment{yegor256} Takes & 1/1 & C3\\%
Long & \Comment{vavr-io} Vavr & 3/3 & C3\\%
\bottomrule%
\end{tabular}
\end{wraptable}
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.
We note that, considering these projects, the modules that do not use
the configuration cited use the sequential configuration \Seq{}.
For example, three modules (=28-25) from Log4J2 use sequential
configuration. It came as a surprise the observation that
no project used distinct configurations in their modules.

>>>>

\noindent\emph{Adoption.}~ We considered two aspects in measuring technology
adoption.  First, we measured usage of parallelism in open-source projects.
Then, we ran a survey with developers to understand the reasons that could
explain resistance to using the technology.\Comment{ For the quantitative
analysis we checked both statically (parsing build files) and dynamically
(monitoring execution of build files) for the presence of parallelization.}
Considering only the projects whose test suites take longer than a minute to
run, we found that only \percentParallelUpdated{} of them use parallelism.  We
also contacted developers from a selection of costly projects that did not use
parallelization to understand the reasons for not using parallelization.\textcolor{red}{[S.J: nao teremos essa dimensao.]}
Dealing with concurrency-related issues (\eg{}, the extra work to organize test
suite to avoid concurrency errors) and the availability of continuous
integration services were the most frequently answered reasons for not
considering parallelization.

@@

We ran the test suite for each subject three times, reporting averaged
execution times in three ranges: tests that run within a minute
(\shortg{}), tests that run in one to five minutes (\medg{}), and
tests that run in five or more minutes (\longg{}). Figure~\ref{fig:rq1-barplot} shows the number of projects in
each group.  As expected, \longg{} and \medg{} projects do not occur
as frequently as \shortg{} projects.  However, they do occur in
relatively high numbers.
Figure~\ref{fig:rq1-boxplot} shows the distribution of execution time of
test suites in each of these groups.
Note that the y-ranges are different.
The distribution associated with the \shortg{} group is the most
unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
group}.
The test suites in this group ran in 15 or less seconds for
over 84.73\% of the cases.\Comment{  Such scenarios constitute the majority of the
cases we analyzed.} Considering the groups \medg{} and \longg{},
however, we found many costly executions.  Nearly 21.84\% of the projects
from the \medg{} group take 3.5 or more minutes to run and nearly 81.40\% of
the projects from the \longg{} group take $\sim$20 minutes to run.  We
found cases in the \longg{} group were execution takes more than 50 minutes
to complete, as can be observed from the outliers in the boxplot.

@@

Column ``\emph{Subject}'' indicates the name of the project, column
\begin{wraptable}{r}{5cm}
\vspace{-4mm}
\caption{Subjects with parallel test execution enabled by default.}
\label{tab:freqmodes-dynamic}
\footnotesize
\centering
\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{llcr}
\toprule
\multirow{2}{*}{\emph{Group}} & \multirow{2}{*}{\emph{Subject}} & \emph{\# of} & \multirow{2}{*}{\emph{Mode}}\\%
   & & \emph{modules} &\\%
\midrule%
Medium & \Comment{alibaba} Nacos & 1/10 & C1\\%
Long & \Comment{apache} Avro & 7/18 & C3\\%
Medium & \Comment{apache} Flink & 108/123 & FC0\\%
Medium & \Comment{apache} OpenNLP & 4/4 & FC0\\%
Medium & \Comment{atmosphere} Nettosphere & 2/2 & FC0\\%
Medium & Chaos & 1/1 & C2\\%
Medium & Cache2k & 10/10 & C2\\%
Medium & \Comment{dropwizard} Metrics & 1/23 & C2\\%
Medium & \Comment{eclipse} Leshan & 11/11 & C2\\%
Medium & \Comment{facebook} Jcommon & 16/16 & FC0\\%
Long & Search Guard & 1/1 & FC0\\%
Long & \Comment{Hazelcast} Jet & 8/8 & FC0\\%
Long & Javaparser & 1/9 & C1\\%
Medium & Jcabi \Comment{jcabi-github} & 1/1 & C3\\%
Long & Optaplanner & 1/13 & FC0\\%
Medium & \Comment{spring-data-cassandra}  Cassandra & 1/1 & C1\\%
Medium & Togglz & 1/34 & C1\\%
Long & Twilio Java & 1/1 & FC0\\%
Long & Vavr & 4/4 & C3\\%
Medium & Rultor & 1/1 & C3\\%
Medium & \Comment{problem-spring-web}  Spring Web & 4/4 & C3\\%
Medium & Zxing & 4/4 & FC0\\%
\bottomrule%
\end{tabular}
\end{wraptable}
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.
We note that, considering these projects, the modules that do not use
the configuration cited use the sequential configuration \Seq{}.
For example, eleven modules (=18-7) from Avro use sequential
configuration. It came as a surprise the observation that
no project used distinct configurations in their modules.
